\documentclass[serif,article,noparskip, en]{agse-thesis}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{indentfirst}
\usepackage{float}

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother
\usepackage[utf8]{inputenc}
\usepackage[ngerman]{babel}
%Math and theorems
\usepackage{amssymb}
%Makes stuff looks nice
\usepackage{amsthm}
\usepackage{microtype}
%Adapts the ratios of the page
\usepackage[headheight=13.6pt, top=3cm, bottom=2.6cm, left=3cm, right=3cm]{geometry}
%adds the nice header and footer
\usepackage{fancyhdr}
%Allows graphics
\usepackage{graphicx}
%long Tables
\usepackage{tabularx}
%nice quotes
\usepackage{csquotes}
%allows to restrict floats to certain regions
\usepackage{placeins}
%counts the lines
\usepackage[displaymath, mathlines]{lineno}
%clickable references
\usepackage{hyperref}
%references in the text
\usepackage[capitalize]{cleveref}
%bibilgraphy
\usepackage[backend=biber]{biblatex}
\usepackage{tikz} 
\usepackage{caption}
\usepackage{graphicx, subfig}
\usepackage{xcolor}
\usepackage[ruled,nolined]{algorithm2e}
\usepackage{biblatex}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\addbibresource{bibliography.bib}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  %numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

% Global parameters, replace with actual values.
\newcommand{\thesisTitle}{Understanding and implementation of the algorithm for three-coloring in triangle-free planar graphs}
% -> You may use \par (but not \\) to format the title. If you do so, you'll
%    need to manually set the 'pdftitle' attribute below.
\newcommand{\studentName}{Qianli Wang}
%===============================================================================
\setlength{\parindent}{2em}
%Specifies theorem environments
%\newtheorem{theorem}[Satz]{Theorem}
\newtheorem{claim}{Claim}
%\newtheorem{corollary}{Conclusion}
%\newtheorem{lemma}{Lemma}
\newtheorem{observation}{Observation}
\theoremstyle{definition}
%\newtheorem{definition}{Definition}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

%Allows correct references to theorem environments
\crefname{theorem}{Satz}{Sätze}
\crefname{corollary}{Folgerung}{Folgerungen}
\crefname{lemma}{Lemma}{Lemmata}
\crefname{observation}{Beobachtung}{Beobachtungen}
\crefname{definition}{Definition}{Definitionen}
\crefname{figure}{Figure}{Figure}
\hypersetup{pdftitle={\thesisTitle}}
\hypersetup{pdfauthor={\studentName}}

% Blind texts, for demonstration only, not part of the actual template
\usepackage{lipsum}

\begin{document}

\coverpage[
    student/id=5338778,
    student/mail=qiaw99@zedat.fu-berlin.de,
    thesis/type=Bachelor Thesis,            % optional, default: Bachelorarbeit
    thesis/group={Work group theoretical computer science},
                                           % optional, default: AGSE
    thesis/advisor={Prof. Dr. László Kozma},           % optional
    thesis/examiner={Prof. Dr. László Kozma},
    thesis/examiner/2={PD Dr. rer. nat. Klaus Kriegel}, % optional
    thesis/date=\today,                    % optional, default: \today
   title/size=\LARGE,      % set this value to overwrite automatic font size
   %abstract/separate       % toggle this to move the abstract to its own page
]
{ % Your abstract here:
    Grötzsch's theorem affirms that every planar graph $G$ in which there is no triangle is 3-colorable. Dvorak, Kawarabayashi, and Thomas have designed a linear-time algorithm relying on the Grötzsch's theorem to find a proper 3-coloring of the given graph.  Compared to Kowalik who used a data structure called "Short Path Data Structure (SPDS)", it avoids complex data structures, which makes it easier to implement. However, because of the difficulty of their paper and complicated proofs, it's really hard to understand it. So we will explain their main idea and proofs with more illustrations and in detail. 
}

\include{declaration}

\cleardoublepage

\tableofcontents

\cleardoublepage

\pagestyle{fancy}

\input{1_introduction}
\input{2_fundamentals}
\input{3_main}
%\input{4_conclusion}

% Refers to file `bibliography.bib`

%\bibliography{bibliography.bib}
\printbibliography

\appendix
\include{5_appendix}

\end{document}